---
title: "Lab 00 - Hello IDS!"
author: "Fergus Towler"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Fergus Towler", "Dimitri", 
           "Harvey", "Eric"),
  github_username = c("mcgregors-garden", "ftowler", "dimir24", 
                      "Capyharav", "HZEric1"), 
  colour = c("powderblue", "purple", "blue", 
             "blue", "red"),
  hobby = c("Hopping", "Tennis", "football", 
            "Drinking", "Warhammer40k"),
  favourite_number = c(2,2, 6, 7, 3)
  )

team_data
```
```{r}
team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Github usernames plotted against favourite number with their favourite colour as the bars colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Github Usernames", 
          y = "Favourite Username",
          title = "Team Info Graph")
```

Allows you to change a plots labels

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The data would be better displayed as a pi chart as it would show the large variance of hobbies while also showing more popular ones without needing a really long chart
